Short-term synaptic plasticity and threshold adaptation act in synergy to give rise to deviance detection in a spiking model of neuronal culture

### 2022-12-07 paper-1/manuscript.tex
Changed corresponding author

\author*[1]{\fnm{Felix Benjamin} \sur{Kern} \orcidA{}}\email{kernfel@gmail.com}

\author[1]{\fnm{Zenas C.} \sur{Chao} \orcidB{}}\email{zenas.c.chao@gmail.com}

>>>>

\author[1]{\fnm{Felix Benjamin} \sur{Kern} \orcidA{}}\email{kernfel@gmail.com}

\author*[1]{\fnm{Zenas C.} \sur{Chao} \orcidB{}}\email{zenas.c.chao@gmail.com}
